\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{LaTeX essay}
\author{Phat Chau}
\date{April 22nd 2025}

\begin{document}
\maketitle
\begin{abstract}
I am writing this essay about my personal history, academic and career goals, and my hobbies and interests. It provides insights into my personal life and motivations by practicing LaTeX.
\end{abstract}
    
    \section{Personal History}
    I am an immigrant who came from Vietnam in 2017. While my life was quiet, I always had a strong curiosity about how things worked. As a child, I always tried to build different buildings and models from Lego. I built everything out of the instruction, and it sparked my lifelong interest in engineering.
    
    \section{Academic and Career Goals}
    I am pursuing a degree in computer science as a senior student with a strong interest in artificial intelligence. I am taking CS-152 to expand my knowledge in Programming Paradigms. I have carried out research to see how vital ethical frameworks are in the deployment of AI~\cite{DBLP:journals/access/NetturKNG25}.
    
    \begin{enumerate}[label=\arabic*.]
      \item Earn a certificate specializing in Machine Learning.
      \item Get a full-time job for tech-role position.
      \item Keep learning from a role at a tech firm that values ethical AI development.
    \end{enumerate}
    
    
    \section{Hobbies and Interests}
    Outside of school, I have many interests. I love hiking, playing sports such as badminton and soccer, and recently started playing pickle ball. I also play the guitar and piano. These hobbies help me maintain a healthy work-life balance.